---
output:
  html_document:
    pandoc_args:
    - +RTS
    - -K64m
    - -RTS
  pdf_document: default
---
DV RProject 1
===
###German Martinez
###GFM367
**For Dr Cannata’s First Homework assignment we were; (1st) instructed to obtain data from the Titanic SQL file online. (2nd) Create an RProject where we will store an .rmd file, some data details, and a few ggplot programs. (3rd) Create an .RMD file to be KnitR-ed into this HTML file to demonstrate our process and progress through the project. (4th) Using the original Titanic Data create a data frame and several different ggplots. (5th) Lastly, come up with one ggplot on your own and explain what is its significance.**

###Steps to reproduce the project:

###First Step
To obtain the data we grabbed the contents from the link provided (in text format) and copy/pasted them onto our SQLDeveloper (which we have an account in) then ran the .txt as a script. Thus creating the Table into our Oracle account.

###Second Step
Go to RStudio and create a new project then add the 3 folders as categorized

###Third Step
Create an .rmd file that will be written then knitR-ed into this html you see right now.2

###Fourth Step
Subset

Summary
```{r}
source("../02 Visualizations/summary.R", echo = TRUE)
```

Table 1
```{r}
source("../02 Visualizations/TitanicTable1.R", echo = TRUE)
```

Table 2
```{r}
source("../02 Visualizations/TitanicTable2.R", echo = TRUE)
```

Table 3
```{r}
source("../02 Visualizations/TitanicTable3.R", echo = TRUE)
```

Table 4
```{r}
source("../02 Visualizations/TitanicTable4.R", echo = TRUE)
```

Table 5
```{r}
source("../02 Visualizations/TitanicTable5.R", echo = TRUE)
```

###Fifth Step
TableNew

```{r}
source("../02 Visualizations/TitanicTableX.R", echo = TRUE)
```
In this new table we can easily see the survived with the gender key. Using this it is easy to see on the table that there is a much larger percentage correlation that most of the woman survived over the men. This is consistant with the common saying "woman and children first" that is expected during evacuation scenarios. 


**German Martinez & Garrett Kreitman
GFM367 , GLK359**


